Software Ticket Quality

### 2017-10-28 proposal/mprop.tex
Added paper reference and layout for modeling bug report quality
Started working on a new paper
Add modeling bug report quality paper

>>>>

\textbf{Modeling Bug Report Quality}\cite{hooimeijer2007modeling}
\begin{itemize}
  \item \textbf{What were the goals?}
    The authors' goal is to present a model that would determine if a bug
    report will be triaged in a given amount of time. Moreover, they are 
    trying to propose features that could help composing a good quality
    bug report.
  \item \textbf{What was the method?}
    They run an analysis on over 27000 bug reports from the Mozilla Firefox
    project, selecting a couple of surface features that could be applied:
      \begin{itemize}
        \item self-reported severity;
        \item readability;
        \item daily load (i.e.\ total number of bug reports that need to be
          dealt with at that point in time);
        \item submitter reputation;
        \item changes over time.
      \end{itemize}
    Afterwards, they ran 4 experiments (i.e.\ validate the assumptions, find
    how much post-submission data is necessary, find the optimal resolved by
    cutoff, evaluate the hypothetical benefit) and analyzed the results to
    see if their model would be beneficial.
  \item \textbf{What did they learn?}
    They found out that linear model, even a simple one, can have 
    better-than-chance predictive power. Also, they came to the conclusion that 
    attachment and comment counts are really valuable for triaging the bug faster,
    compared to, for example, patch count. Moreover, the readability of a bug is
    important as it proved to influence the duration of the triaging process. 
  \item \textbf{Relevance to our work}: the authors' goal was quite similar to ours
    as they are trying to find out which features make for a good quality bug 
    report. Moreover, they are also using programmatic analysis instead of
    interviews with developers to produce the results, which is the same approach
    we are aiming for in our research.
\end{itemize}
